HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-09-14 paper/main.tex
All authors equally

\author{
  Alexandra Birch\textsuperscript{1}, Omri Abend\textsuperscript{2}, Ond{\v{r}}ej Bojar\textsuperscript{3},
  Barry Haddow\textsuperscript{1}\\
\textsuperscript{1}School of Informatics, University of Edinburgh\\
\textsuperscript{2}School of Computer Science and Engineering, Hebrew University of Jerusalem\\
\textsuperscript{3} Charles University in Prague, Faculty of Mathematics and Physics\\
\texttt{a.birch@ed.ac.uk, oabend@cs.huji.ac.il}\\
\texttt{bojar@ufal.mff.cuni.cz, bhaddow@inf.ed.ac.uk}\\
}

@@

>>>>

\author{
  Alexandra Birch\textsuperscript{1}, Omri Abend\textsuperscript{2}, Ond{\v{r}}ej Bojar\textsuperscript{3},
  Barry Haddow\textsuperscript{1*}\\
\textsuperscript{1}School of Informatics, University of Edinburgh\\
\textsuperscript{2}School of Computer Science and Engineering, Hebrew University of Jerusalem\\
\textsuperscript{3} Charles University in Prague, Faculty of Mathematics and Physics\\
\texttt{a.birch@ed.ac.uk, oabend@cs.huji.ac.il}\\
\texttt{bojar@ufal.mff.cuni.cz, bhaddow@inf.ed.ac.uk}\\
}

@@

\let\thefootnote\relax\footnotetext{*All authors contributed equally to this work.}
